\begin{thebibliography}{99}
\bibitem{ref1} 王友发, 等. 中国居民肥胖防治专家共识[J]. 中国预防医学杂志, 2022, 23(5): 321--339.
\bibitem{ref2} Wu Y. Overweight and obesity in China[J]. BMJ, 2006, 333(7564): 362--363.
\bibitem{ref3} 国家卫生计生委. 中国居民营养与慢性病状况报告（2015年）[R]. 北京: 国家卫生计生委, 2015.
\bibitem{ref4} 国家卫生健康委. 中国居民营养与慢性病状况报告（2020年）[R]. 北京: 国家卫生健康委, 2020.
\bibitem{ref5} Hu J, Xie J, Liu B, et al. Major risk factors of obesity in China and recommendations for future prevention and control efforts: a systematic review and meta-analysis[J]. The Lancet Regional Health -- Western Pacific, 2026, 68: 101833. DOI: 10.1016/j.lanwpc.2026.101833.
\bibitem{ref6} Gompertz B. On the nature of the function expressive of the law of human mortality[J]. Philosophical Transactions of the Royal Society of London, 1825, 115: 513--583.
\bibitem{ref7} Verhulst P F. Notice sur la loi que la population suit dans son accroissement[J]. Correspondance Math\'{e}matique et Physique, 1838, 10: 113--121.
\bibitem{ref8} Levenberg K. A method for the solution of certain non-linear problems in least squares[J]. Quarterly of Applied Mathematics, 1944, 2(2): 164--168.
\bibitem{ref9} 健康中国行动推进委员会. 健康中国行动（2019--2030年）[Z]. 北京, 2019.
\bibitem{ref10} Varkevisser R D M, van Stralen M M, Kroeze W, et al. Determinants of weight loss maintenance: a systematic review[J]. Obesity Reviews, 2019, 20(2): 171--211.
\bibitem{ref11} Lemstra M, Bird Y, Nwankwo C, et al. Weight loss intervention adherence and factors promoting adherence: a meta-analysis[J]. Patient Preference and Adherence, 2016, 10: 1547--1559.
\bibitem{ref12} Neri L C L, Mariotti F, Guglielmetti M, et al. Dropout in cognitive behavioral treatment in adults living with overweight and obesity: a systematic review[J]. Frontiers in Nutrition, 2024, 11: 1250683.
\bibitem{ref13} Hall K D, Kahan S. Maintenance of lost weight and long-term management of obesity[J]. Medical Clinics of North America, 2018, 102(1): 183--197.
\bibitem{ref14} Ji L, Mu Y, Chang C, et al. Perceptions, attitudes and barriers to effective obesity care among people living with obesity and healthcare professionals in China: The ACTION-China study[J]. Diabetes, Obesity and Metabolism, 2024, 26(10): 4694--4704.
\bibitem{ref15} 国家卫生健康委. 肥胖症诊疗指南（2024年版）[R]. 北京: 国家卫生健康委, 2024.
\bibitem{ref16} 国家卫生健康委. 体重管理指导原则（2024年版）[R]. 北京: 国家卫生健康委, 2024.
\bibitem{ref17} Diakoulaki D, Mavrotas G, Papayannakis L. Determining objective weights in multiple criteria problems: The CRITIC method[J]. Computers \& Operations Research, 1995, 22(7): 763--770.
\bibitem{ref18} Hwang C L, Yoon K. Multiple Attribute Decision Making: Methods and Applications[M]. Berlin: Springer-Verlag, 1981.
\bibitem{ref19} 国家卫生健康委. 成人肥胖食养指南（2024年版）[R]. 北京: 国家卫生健康委, 2024.
\bibitem{ref20} 中国营养学会. 中国居民膳食指南（2022）：平衡膳食八准则[Z]. 北京: 中国营养学会, 2022.
\bibitem{ref21} 《中国人群身体活动指南》编写委员会. 中国人群身体活动指南（2021）[J]. 中国公共卫生, 2022, 38(2): 129--130.
\bibitem{ref22} 国家卫生健康委等16部门. 关于印发“体重管理年”活动实施方案的通知[Z]. 北京, 2024.
\bibitem{ref23} World Health Organization. Physical activity: fact sheet[Z]. Geneva: World Health Organization, 2024.
\bibitem{ref24} European Environment Agency. Environmental indicators: Typology and overview[R]. Copenhagen: European Environment Agency, 1999.
\bibitem{ref25} United Nations, Department of Economic and Social Affairs, Population Division. World Population Prospects 2024[R]. New York: United Nations, 2024.
\end{thebibliography}

% ==================== 附录 ====================
